---
title: "Weight of Fish"
author: "Dom Ciriello"
date: "20210406"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```
```{r}
Fishdata=read.csv(file="Fish.csv")
```



# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  

# Perch
## Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->


```{r}
Perchdata=filter(Fishdata, Species=="Perch")
Perchdata=subset (Perchdata, select=-Species)
```

## Inferential Results

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perchdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
##Which is best??  

The model with Height and Width is the most accurate per the graph above because it has the highest adjusted R-Squared value.

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~Height+Width,data=Perchdata)
fullup <- lm(Weight~.,data=Perchdata)
summary(best.model)
```
The p-value for this is incredibly small which means that it did not happen merely by chance. It is extremely accurate.

```{r}
anova(fullup, best.model)
```

The p value here is large which means that there is no major difference between using 2 variables and all the variables.

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->



# Bream

## Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r}
Breamdata=filter(Fishdata, Species=="Bream")
Breamdata=subset (Breamdata, select=-Species)
```

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Breamdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
##Which is best??  

The overall best model is the one with 3 variables (Length 1, Height and Width). However, the best model with only 2 variables is the one with Length 2 and Height. This is based on the highest adjusted R-Squared value.

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~Length2+Height,data=Breamdata)
fullup <- lm(Weight~.,data=Breamdata)
summary(best.model)
```
The p-value for this one is extremely small too, so it is highly unlikely that it happened by chance.

```{r}
anova(fullup, best.model)
```
The p value here is large which means that there is no major difference between using 2 variables and all the variables.

# Smelt
## Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r}
Smeltdata=filter(Fishdata, Species=="Smelt")
Smeltdata=subset (Smeltdata, select=-Species)
```

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Smeltdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
##Which is best??  

Overall, the most accurate model for Smelt is the one that takes into account: Length 1, Length 2, Height and Width. However, if we are limited to only 2 variables, the most accurate model we could make would consist of Length 2 and Width.

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~Length2+Width,data=Smeltdata)
fullup <- lm(Weight~.,data=Smeltdata)
summary(best.model)
```
This p-value is very small which means that it did not happen by chance. It is a very accurate model.

```{r}
anova(fullup, best.model)
```
The p value here is large which means that there is no major difference between using 2 variables and all the variables.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Overall, the p-value comparing the 2-variable models and the models with all variables was very high which means we fail to reject the null hypothesis. There is really no difference in using the best 2 variables and using all the available variables for predicting the weight of Perch, Bream and Smelt.